---
title: "coding club"
output: html_document
---

```{r}
# Question: which library does what?
library(nat)
library(fafbseg)
library(tidyverse)
library(igraph)
library(arrow)
library(coconatfly)
library(rgl)
#devtools::install_github("rstats-db/RSQLite")

#simple_python(pyinstall = 'none', pkgs = 'numpy')
#simple_python('full')
#reticulate::import('fafbseg')
```
Prompt 1: 
Choose a neuron, whatever you like as long as it has upstream and downstream partners.

```{r}

LC9n = "720575940617678897"

```

Get its top 3 downstream partners and upstream partners (via fafbseg or natverse)

```{r}

# The problem with the following code is that it doesn't give synapse xyz coordinates needed for later in the task.

#cf_partners(cf_ids(flywire =LC9n), partners = 'in') %>%
  #slice_head(n=3) %>% 
  #select(pre_id) -> LC9_3in

#cf_partners(cf_ids(flywire = LC9n), partners = 'o') %>% 
  #slice_head(n=3) %>% 
  #select(post_id) -> LC9_3o

```

```{r}

# The function flywire_partners() with argument details = TRUE has columns with xyz coordinates of pre and post synapses.

#input partners
flywire_partners(LC9n, partners = 'i', details = TRUE) %>%
  #to remove autapses
  filter(pre_id != post_id) %>% 
  #conventional cut off point to remove fake synapses
  filter(cleft_scores > 50) %>% 
  group_by(pre_id) %>% 
  mutate(weight=n()) %>% 
  #good coding practice to always ungroup() after group_by() (see https://bookdown.org/yih_huynh/Guide-to-R-Book/groupby.html). 
  ungroup() %>% 
  arrange(desc(weight)) -> LC9_in

LC9_in %>% 
  distinct(pre_id, .keep_all = TRUE) %>% 
  slice_head(n=3) -> LC9_3in

#output partners
flywire_partners(LC9n, partners = 'o', details = TRUE) %>%
  #to remove autapses
  filter(pre_id != post_id) %>% 
  filter(cleft_scores > 50) %>% 
  group_by(post_id) %>% 
  mutate(weight=n()) %>% 
  ungroup() %>%
  arrange(desc(weight)) -> LC9_o

LC9_o %>% 
  distinct(post_id, .keep_all = TRUE) %>% 
  slice_head(n=3) -> LC9_3o

```

Using natverse/Navis, plot all 7 neurons in either 2D or 3D:
main one in red
upstream 3 in blue
downstream 3 in yellow

```{r}

# to plot 3D meshes, use function save_cloudvolume_meshes or fafbseg::read_cloudvolume_meshes()
# to plot 2D skeletons, use function read_l2skel or read_l2dp 

read_l2skel(LC9n) %>%
  plot3d(col = "red")

LC9_3in %>% 
  select(pre_id) %>% 
  read_l2skel() %>% 
  plot3d(col = "blue")

LC9_3o %>% 
  select(post_id) %>% 
  read_l2skel() %>% 
  plot3d(col = "yellow")

```

also plot all of the synapse locations between the main neuron and the other 6 as white dots

```{r}

# Yijie recommends to try and use function points3d(), use add = TRUE argument to plot in the same window

#adding input synapses

LC9_in %>% 
  filter(pre_id %in% LC9_3in$pre_id) 

points3d(LC9_in$pre_x, LC9_in$pre_y, LC9_in$pre_z, col = 'green')

#adding output synapses

LC9_o %>% 
  filter(pre_id %in% LC9_3o$pre_id) 

points3d(LC9_o$pre_x, LC9_o$pre_y, LC9_o$pre_z, col = 'black')

```

Now choose a cell type, and get all the neurons in that cell type from flytable.

```{r}
LC9=flytable_meta('LC9%')
LC9 %>% 
  select(root_id)
```


Fetch all the upstream and downstream partners of all the neurons in that class.

What are the top 3 upstream classes and top 3 downstream classes?

Do any of the upstream or downstream classes also directly interact?

try and do heatmap to show connectivity
